Missing data: Current practice in football research and recommendations for improvement

### 2020-09-10 paper/paper.Rmd
move supplement 3 into main text

aq_vis_miss <- vis_miss(airquality)

>>>>

# Aim of this section:
# Simulate data from a real data set, insert missing
# Mini study: predicting super coach scores

d <- get_afltables_stats(start_date = "2020-01-01", 
                         end_date = "2020-09-04")

data <-
  d %>% select(
    ID,
    Round,
    First.name,
    Surname,
    Kicks,
    Handballs,
    Marks,
    Hit.Outs,
    Contested.Possessions,
    Uncontested.Possessions
  )
#View(data)

df <- get_footywire_stats(10286:10290) # Get the fantasy scores

# View(df)
df #%>% View("footywire dataset")

# Generate the y-variable
fit <- lm(AF ~ K + HB, data = df)
summary(fit)
data %>% mutate(fanasty_score = 4.106*Kicks + 2.175*Handballs)

# Completed dataset
# Drop a team
No_Richmond <- df %>% filter(Team!="Richmond")
sort(unique(No_Richmond$Team))
sort(unique(df$Team))

# Impute missing values
df_first_try <- mice::ampute(data = df[,10:43])
df_first_try <- df_first_try$amp

# Examples of presenting of missing values
naniar::vis_miss(df_first_try)
naniar::vis_miss(df_first_try)
naniar::gg_miss_fct(x = riskfactors, fct = marital)

# Example write up of missing values

```{r}
aq_vis_miss <- vis_miss(airquality)
